\section{Conclusion}

We have presented a computational analysis of the Kaladont word chain game across 25 languages, using lemmatised word lists derived from the English Wiktionary and Monte Carlo simulation. The results show that chain playability varies dramatically across languages, with Serbo-Croatian and Georgian producing the longest chains (means of 40.4 and 34.9 words respectively) and Greek and Hindi the shortest (means of 2.0 and 2.4). Language family membership is a partial but imperfect predictor of playability: South Slavic languages consistently rank high, Germanic languages cluster in the middle, but Baltic languages diverge despite their relatedness.

\subsection{Limitations}

Several limitations should be noted. First, all data derives from the English Wiktionary, which has uneven coverage across languages. Smaller or less internationally prominent languages are under-represented, which both reduces lexicon size and may bias the sample toward internationally known vocabulary. Second, despite extensive filtering, the word lists remain imperfect: obscure loanwords, archaic forms, and residual inflected forms that appear as standalone Wiktionary entries can pass through. Third, the simulation assumes that any word in the lexicon is equally accessible to a player, whereas real players have finite and uneven vocabulary. Fourth, the game is simulated without the strategic element of deliberately choosing a word whose ending is hard to continue — the simulation selects successors uniformly at random.

\subsection{Future Work}

Future directions include: (1) sourcing word lists from native-language Wiktionary editions for better coverage of smaller languages; (2) modelling optimal play, where each player selects the word whose ending has the fewest continuations, to estimate the game length under adversarial conditions; (3) analysing the structure of the word-chain graph directly — its degree distribution, connected components, and the identity of the hub bigrams that sustain long chains; (4) extending the study to non-Indo-European language families.

\paragraph{Code and data.} The simulation code is available at \url{https://github.com/viktor-ktorvi/kaladont}.
